Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-25 chap-intro.tex
Leave "notation" uncountable

To simplify navigation, we number all sorts of ``theorems'' (including here
definitions, remarks, even examples or notations)
per-chapter with counters including section numbers. For
instance, \cref{def:inc-semantics} is the first such item in
\cref{ch:derive-formally}, followed by \cref{thm:derive-correct}, and they both
appear in \cref{sec:correct-derive}. And we can be sure that \cref{lem:derive-typing}
comes after both ``theorems'' because of its number, even if they are of different sorts.

>>>>

To simplify navigation, we number all sorts of ``theorems'' (including here
definitions, remarks, even examples or descriptions of notation)
per-chapter with counters including section numbers. For
instance, \cref{def:inc-semantics} is the first such item in
\cref{ch:derive-formally}, followed by \cref{thm:derive-correct}, and they both
appear in \cref{sec:correct-derive}. And we can be sure that \cref{lem:derive-typing}
comes after both ``theorems'' because of its number, even if they are of different sorts.
